Title: Weeks 1 and 2
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2018-08-27 08:00
Tags: class notes
Slug: week-01-02-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
```

[What are the computational and data sciences?]{.h2}

[Videos]{.h3}

**01 - What are the computational and data sciences - Prologue**

```{r what-are-comput-data-sci-01-prologue, echo = FALSE}
vembedr::embed_youtube(id = "c5SiNBP88BM", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**02 - What are the computational and data sciences - Science**

```{r what-are-comput-data-sci-02-science, echo = FALSE}
vembedr::embed_youtube(id = "fxLFfuW4eag", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**03 - What are the computational and data sciences - Data Overview**

```{r what-are-comput-data-sci-03-data-overview, echo = FALSE}
vembedr::embed_youtube(id = "t7iEMTkfY6g", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**04 - What are the computational and data sciences - Data Sampling**

```{r what-are-comput-data-sci-04-data-sampling, echo = FALSE}
vembedr::embed_youtube(id = "kGlrYxTDGh8", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**05 - What are the computational and data sciences - Computation**

```{r what-are-comput-data-sci-05-computation, echo = FALSE}
vembedr::embed_youtube(id = "7mhehSq959k", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h3}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Science]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Data overview]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - Data sampling]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Computation]{.card-downloads-format}][slides-04]
:::

[slides-01]: /doc/week01_what_are_comput_data_sci_01_science.pdf
[slides-02]: /doc/week01_what_are_comput_data_sci_02_data_overview.pdf
[slides-03]: /doc/week01_what_are_comput_data_sci_03_data_sampling.pdf
[slides-04]: /doc/week01_what_are_comput_data_sci_04_computation.pdf
