Title: Week 3
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2018-09-10 08:00
Tags: class notes
Slug: week-03-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Reproducible toolbox]{.h2}

[Module exercises]{.h3}

::: {.no-bullets}
*   [`r icon_laptop` &nbsp; [DataCamp exercises (Week 3)]{.card-downloads-format}][module-exercises]
:::
<div style="margin-bottom: 1em"></div>

[Videos]{.h3}

**01 - Reproducible toolbox - Reproducibility in science**

```{r what-are-comput-data-sci-01-prologue, echo = FALSE}
vembedr::embed_youtube(id = "-Pw-z_rROlw", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**02 - Reproducible toolbox - Reproducible research toolkit**

```{r what-are-comput-data-sci-02-science, echo = FALSE}
vembedr::embed_youtube(id = "GicSJT_VorM", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h3}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Reproducibility in science]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Reproducible research toolkit]{.card-downloads-format}][slides-02]
:::

[slides-01]:        /doc/week03_reproducible_toolbox_01_reproducibility_in_science.pdf
[slides-02]:        /doc/week03_reproducible_toolbox_02_reproducible_research_toolkit.pdf
[module-exercises]: /assignments/datacamp-exercises-week-3
