Title: Week 9
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2018-10-22 08:00
Tags: class notes
Slug: week-09-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Data reshaping]{.h2}

[Homework assignment]{.h3}

::: {.no-bullets}
*   [`r icon_pencil` &nbsp; [Homework 2 (continued)]{.card-downloads-format}][homework-2-assignment] (Due: Oct-26)
:::
<div style="margin-bottom: 1em"></div>

[Module exercises]{.h3}

::: {.no-bullets}
*   [`r icon_laptop` &nbsp; [DataCamp exercises (Week 9)]{.card-downloads-format}][module-exercises] (Due: Oct-29)
:::
<div style="margin-bottom: 1em"></div>

[Readings]{.h3}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Week 9 readings]{.card-downloads-format}][readings] (Due: Oct-28)
:::
<div style="margin-bottom: 1em"></div>

[Videos]{.h3}

::: {.no-bullets}
*   ***To be posted...***
:::

<!--
(Due: Oct-28)

**Data reshaping - 01 - Principles of tidy data**

```{r data-reshaping-01-principles-of-tidy-data, echo = FALSE, eval = FALSE}
vembedr::embed_youtube(id = "", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data reshaping - 02 - The gather function**

```{r data-reshaping-02-the-gather-function, echo = FALSE, eval = FALSE}
vembedr::embed_youtube(id = "", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data reshaping - 03 - The spread function**

```{r data-reshaping-03-the-spread-function, echo = FALSE, eval = FALSE}
vembedr::embed_youtube(id = "", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data reshaping - 04 - The separate function**

```{r data-reshaping-04-the-separate-function, echo = FALSE, eval = FALSE}
vembedr::embed_youtube(id = "", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data reshaping - 05 - The unite function**

```{r data-reshaping-05-the-unite-function, echo = FALSE, eval = FALSE}
vembedr::embed_youtube(id = "", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

-->

[Slides]{.h3}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Principles of tidy data]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - The [gather]{.monospace} function]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - The [spread]{.monospace} function]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - The [separate]{.monospace} function]{.card-downloads-format}][slides-04]

*   [`r icon_pdf` &nbsp; [05 - The [unite]{.monospace} function]{.card-downloads-format}][slides-05]
:::

[readings]:              /assignments/week-09-readings/
[slides-01]:             /doc/week09_data_reshaping_01_principles_of_tidy_data.pdf
[slides-02]:             /doc/week09_data_reshaping_02_the_gather_function.pdf
[slides-03]:             /doc/week09_data_reshaping_03_the_spread_function.pdf
[slides-04]:             /doc/week09_data_reshaping_04_the_separate_function.pdf
[slides-05]:             /doc/week09_data_reshaping_05_the_unite_function.pdf
[module-exercises]:      /assignments/datacamp-exercises-week-9
[homework-2-assignment]: /assignments/homework-2/
