Title: Week 4
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2018-09-17 08:00
Tags: class notes
Slug: week-04-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen_square <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
```

[Data visualization]{.h2}

[Mini-assignments]{.h3}

::: {.callout .secondary}
[First-time RStudio Server setup]{.h4}

**Important!** Follow **all** the directions in the repository linked below **before** starting work on the two mini-assignments.

:::: {.no-bullets}
*   [`r icon_github` &nbsp; [RStudio Server Configuration repository]{.card-downloads-format}][rstudio-configuration] 
::::
:::

::: {.no-bullets}
*   [`r icon_pen_square` &nbsp; [R Markdown mini-assignment]{.card-downloads-format}][r-markdown-mini-assignment]

*   [`r icon_pen_square` &nbsp; [Visualization mini-assignment]{.card-downloads-format}][visualization-mini-assignment]
:::
<div style="margin-bottom: 1em"></div>

[Module exercises]{.h3}

::: {.no-bullets}
*   [`r icon_laptop` &nbsp; [DataCamp exercises (Week 4)]{.card-downloads-format}][module-exercises]
:::
<div style="margin-bottom: 1em"></div>

[Readings]{.h3}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Week 4 readings]{.card-downloads-format}][readings]  
:::
<div style="margin-bottom: 1em"></div>

[Videos]{.h3}

**Data visualization - 01 - Data visualization as communication**

```{r data-visualization-01-communication, echo = FALSE}
vembedr::embed_youtube(id = "W5Fnc4U3sS4", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data visualization - 02 - Examining numerical data**

```{r data-visualization-02-examining-numerical-data, echo = FALSE}
vembedr::embed_youtube(id = "Dtveq_kYlKQ", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h3}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Data visualization as communication]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Examining numerical data]{.card-downloads-format}][slides-02]
:::

[readings]:                      /assignments/week-04-readings/
[slides-01]:                     /doc/week04_data_visualization_01_data_visualization_as_communication.pdf
[slides-02]:                     /doc/week04_data_visualization_02_examining_numerical_data.pdf
[module-exercises]:              /assignments/datacamp-exercises-week-4
[rstudio-configuration]:         https://github.com/mason-fa18-cds-101-dl1/configure-rstudio-server
[r-markdown-mini-assignment]:    /assignments/rmarkdown-mini-assignment/
[visualization-mini-assignment]: /assignments/visualization-mini-assignment/
