Title: Week 6
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2018-10-01 08:00
Tags: class notes
Slug: week-06-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Data transformation]{.h2}

[Homework assignment]{.h3}

::: {.no-bullets}
*   [`r icon_pencil` &nbsp; [Homework 1 (continued)]{.card-downloads-format}][homework-1-assignment]
:::
<div style="margin-bottom: 1em"></div>

[Module exercises]{.h3}

::: {.no-bullets}
*   [`r icon_laptop` &nbsp; [DataCamp exercises (Week 6)]{.card-downloads-format}][module-exercises]
:::
<div style="margin-bottom: 1em"></div>

[Readings]{.h3}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Week 6 readings]{.card-downloads-format}][readings]
:::
<div style="margin-bottom: 1em"></div>

[Videos]{.h3}

::: {.callout .secondary}
[Starter files for lecture demos]{.h4}

Below is the download link that you should click to get a copy of the starter files you'll need to have when following along with the lecture demos. 

::::: {.no-bullets}
*   [`r icon_github` &nbsp; [dplyr demonstration starter files]{.card-downloads-format}][dplyr-demo-repo]
:::::
:::

**Data transformation - 01 - What is data wrangling?**

```{r data-transformation-01-what-is-data-wrangling, echo = FALSE}
vembedr::embed_youtube(id = "j8tKN7Iw5dw", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data transformation - 02 - The presidential dataset**

```{r data-visualization-02-the-presidential-dataset, echo = FALSE}
vembedr::embed_youtube(id = "wP6xGaTdfVc", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data transformation - 03 - The select function**

```{r data-visualization-03-the-select-function, echo = FALSE}
vembedr::embed_youtube(id = "bfmMYUOWnls", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data transformation - 04 - The pipe operator**

```{r data-visualization-04-the-pipe-operator, echo = FALSE}
vembedr::embed_youtube(id = "SdrBENv3F-s", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data transformation - 05 - The arrange function**

```{r data-visualization-05-the-arrange-function, echo = FALSE}
vembedr::embed_youtube(id = "9Hnz8KEBCUc", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data transformation - 06 - The slice function**

```{r data-visualization-06-the-slice-function, echo = FALSE}
vembedr::embed_youtube(id = "m3lvPn8oP2E", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data transformation - 07 - Boolean logic**

```{r data-visualization-07-boolean-logic, echo = FALSE}
vembedr::embed_youtube(id = "_nVGIkzf8fg", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data transformation - 08 - The filter function**

```{r data-visualization-08-the-filter-function, echo = FALSE}
vembedr::embed_youtube(id = "BnscboiLaUM", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h3}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - What is data wrangling?]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - The [presidential]{.monospace} dataset]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - The [select]{.monospace} function]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - The pipe [%>%]{.monospace} operator]{.card-downloads-format}][slides-04]

*   [`r icon_pdf` &nbsp; [05 - The [arrange]{.monospace} function]{.card-downloads-format}][slides-05]

*   [`r icon_pdf` &nbsp; [06 - The [slice]{.monospace} function]{.card-downloads-format}][slides-06]

*   [`r icon_pdf` &nbsp; [07 - Boolean logic]{.card-downloads-format}][slides-07]

*   [`r icon_pdf` &nbsp; [08 - The [filter]{.monospace} function]{.card-downloads-format}][slides-08]
:::

[readings]:              /assignments/week-06-readings/
[slides-01]:             /doc/week06_data_transformation_01_what_is_data_wrangling.pdf
[slides-02]:             /doc/week06_data_transformation_02_the_presidential_dataset.pdf
[slides-03]:             /doc/week06_data_transformation_03_the_select_function.pdf
[slides-04]:             /doc/week06_data_transformation_04_the_pipe_operator.pdf
[slides-05]:             /doc/week06_data_transformation_05_the_arrange_function.pdf
[slides-06]:             /doc/week06_data_transformation_06_the_slice_function.pdf
[slides-07]:             /doc/week06_data_transformation_07_boolean_logic.pdf
[slides-08]:             /doc/week06_data_transformation_08_the_filter_function.pdf
[dplyr-demo-repo]:       https://classroom.github.com/a/_Ylvc7ue
[module-exercises]:      /assignments/datacamp-exercises-week-6
[homework-1-assignment]: /assignments/homework-1/
