Title: Week 11
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2018-11-05 08:00
Tags: class notes
Slug: week-11-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Data distributions]{.h2}

[Homework assignment]{.h3}

::: {.no-bullets}
*   [`r icon_pencil` &nbsp; [Homework 2 (Group)]{.card-downloads-format}][homework-2-group-assignment] (Due: Nov-09)
:::
<div style="margin-bottom: 1em"></div>

[Readings]{.h3}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Week 11 readings]{.card-downloads-format}][readings] (Due: Nov-11)
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h3}

(Due: Nov-11)

**Data distributions - 01 - Quantifying data distributions**

```{r data-distributions-01-quantifying-data-distributions, echo = FALSE}
vembedr::embed_youtube(id = "BL5Bt-nI22k", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data distributions - 02 - Quantifying data distributions in R**

```{r data-distributions-02-quantifying-data-distributions-in-r, echo = FALSE}
vembedr::embed_youtube(id = "tvUw91TrWO4", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data distributions - 03 - Probability mass functions**

```{r data-distributions-03-probability-mass-functions, echo = FALSE}
vembedr::embed_youtube(id = "xbLim5imqe4", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data distributions - 04 - Cumulative distribution functions**

```{r data-distributions-04-cumulative-distribution-functions, echo = FALSE}
vembedr::embed_youtube(id = "WC3YL8Npujw", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h3}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Quantifying data distributions]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Quantifying data distributions in R]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - Probability mass functions]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Cumulative distribution functions]{.card-downloads-format}][slides-04]
:::

[readings]:                    /assignments/week-11-readings/
[slides-01]:                   /doc/week11_data_distributions_01_quantifying_data_distributions.pdf
[slides-02]:                   /doc/week11_data_distributions_02_quantifying_data_distributions_in_r.pdf
[slides-03]:                   /doc/week11_data_distributions_03_probability_mass_functions.pdf
[slides-04]:                   /doc/week11_data_distributions_04_cumulative_distribution_functions.pdf
[homework-2-group-assignment]: /assignments/homework-2-group/
