Title: Week 5
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2018-09-24 08:00
Tags: class notes
Slug: week-05-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Data visualization]{.h2}

[Homework assignment]{.h3}

::: {.no-bullets}
*   [`r icon_pencil` &nbsp; [Homework 1]{.card-downloads-format}][homework-1-assignment]
:::
<div style="margin-bottom: 1em"></div>

[Module exercises]{.h3}

::: {.no-bullets}
*   [`r icon_laptop` &nbsp; [DataCamp exercises (Week 5)]{.card-downloads-format}][module-exercises]
:::
<div style="margin-bottom: 1em"></div>

[Readings]{.h3}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Week 5 readings]{.card-downloads-format}][readings]
:::
<div style="margin-bottom: 1em"></div>

[Videos]{.h3}

**Data visualization - 03 - Describing visualizations**

```{r data-visualization-03-describing, echo = FALSE}
vembedr::embed_youtube(id = "HVFek-6iz-M", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Data visualization - 04 - Data visualization with ggplot2**

```{r data-visualization-04-data-visualization-with-ggplot2, echo = FALSE}
vembedr::embed_youtube(id = "pmjM0mz_1Es", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h3}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [03 - Describing visualizations]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Data visualization with ggplot2]{.card-downloads-format}][slides-04]
:::

[readings]:              /assignments/week-05-readings/
[slides-03]:             /doc/week05_data_visualization_03_describing_visualizations.pdf
[slides-04]:             /doc/week05_data_visualization_04_data_visualization_with_ggplot2.pdf
[module-exercises]:      /assignments/datacamp-exercises-week-5
[homework-1-assignment]: /assignments/homework-1/
