Title: Homework 2 (Group)
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2018-11-09 23:59
Tags: homework
Slug: homework-2-group
Summary: Collaborate with your assigned group members to turn your individual submissions for Homework 2 into a data exploration report.
Show_summary: true
Show_link: true

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, eval = TRUE, fig.width = 5,
  fig.asp = 0.618, out.width = "70%", dpi = 120,
  fig.align = "center", cache = TRUE, dev = "svg"
)
icon_html5 <- '<i class="fab fa-html5" data-fa-transform="grow-8"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_square <- '<i class="far fa-square" data=fa=transform="grow-8"></i>&nbsp;'
```

[**Group submissions due:** November 9, 2018 @ 11:59pm]{.h3}

::: {.no-bullets}
*   [`r icon_github` Github Classroom repo for **Homework 2 (Group)**][github-classroom-repo]
:::

## Instructions

The Homework 2 questions and instructions from last time are available here: <http://fall18.cds101.com/assignments/homework-2/>

### Overview

Your primary task is to use the R Markdown file [homework\_2\_group.Rmd]{.monospace} to write up your group's answers to the homework assignment.
Grades for the group submissions will, in addition to correctness, be based on document formatting, visualization quality, writing quality, and code style.
**This means that your group submission is to be written in the style of a exploratory data report, meaning:**

*   Each exercise must be written up using full sentences such that it is clear what question is being answered.

*   There needs to be plain text above each code block explaining what you are doing, and the code blocks should be organized.

*   The R Markdown file **must** knit without error and generate a PDF file, and the final PDF output must look nice, clean, and be easy to read.

### Participation

Credit for group participation will be determined using the following sources:

1.  A [CONTRIBUTIONS.md]{.monospace} file distributed with your group repository

2.  Commit history on GitHub

3.  Discussion history in your group's private Slack channel

**Each group will need to fill out the [CONTRIBUTIONS.md]{.monospace} file as part of their submission.**
This file is where where each group member lists what he or she contributed to the final submission.
Read the section **[Fill out the [CONTRIBUTIONS.md]{.monospace} file](#fill-out-the-contributions.md-file)** for more details on how this works.

#### Google Docs

If your group used an external document to coordinate and organize your work, such as a Google Doc, then that can also count as evidence of participation, **provided there is a visible writing history and I can identify which student is responsible for each edit.**
This will require you to share the relevant file with the email address [jglasbr2@gmu.edu]{.monospace} and give me full privileges on the document so that I can review the document's editing history.
Please note that anonymous edits to Google Docs documents cannot be used as participation evidence, because I have no way to verify the account responsible for the added content.
Also, for similar reasons, offline documents traded back and forth via email cannot be accepted as evidence of participation.

### How to answer the questions as a group

The following is a checklist you may follow to help you get started with answering the questions as a group:

::: {.no-bullets}
*   `r icon_square` Share and discuss your individual submissions for Homework 2 with your assigned group and come to a consensus about the correct answer for each question.

*   `r icon_square` As a group, decide who will be responsible for writing the answer to each question.

*   `r icon_square` **(Important)** Before you start, make a copy of [homework\_2\_group.Rmd]{.monospace} and **rename the copied file** to include your last name. For example, if your last name is Smith, then your file copy should be renamed to [homework\_2\_group\_smith.Rmd]{.monospace}.

*   `r icon_square` Commit and push your copied file to GitHub. If you need a refresher on how to interact with GitHub, watch the linked video below:<br>

    ```{r data-visualization-02-the-presidential-dataset, echo = FALSE}
    vembedr::embed_youtube(id = "wP6xGaTdfVc", width = 640, height = 480, allowfullscreen = TRUE, frameborder = 0)
    ```

*   `r icon_square` Place your write-ups for your questions in your file. Again, if my last name was Smith, and I agreed to write-up the answers to questions 4, 5, and 6, then I would open up [homework\_2\_group\_smith.Rmd]{.monospace} and put my answers there. When I'm done, I would save my file, then commit and push my work to GitHub.
:::

### How to edit and merge your answers into the group submission

While you will be writing your answers in separate files, eventually the group will need to merge in everyone's answers into the [homework\_2\_group.Rmd]{.monospace} document.
The following checklist may help with this:

::: {.no-bullets}
*   `r icon_square` Select an editor to be in charge of merging everyone's answers into the final document [homework\_2\_group.Rmd]{.monospace}. Because the editor needs to take care of extra work to prepare the document for submission, it is reasonable if he or she does not contribute write-ups for as many of the questions as the rest of the group (for example, if everyone else answers three questions, the editor may only answer two).

*   `r icon_square` The editor should ensure that everyone has committed and pushed their answers to GitHub so they can copy and paste in each contribution.

*   `r icon_square` The editor needs to make sure that the final submission reads like a coherent document and that the writing style and code style are uniform across all the answers. In other words, it should read like a single person answered all the questions, not a group of four people.

*   `r icon_square` The editor will be in charge of of committing and pushing the final R Markdown file to GitHub, knitting to PDF, and uploading the PDF file on Blackboard.
:::

### Fill out the [CONTRIBUTIONS.md]{.monospace} file

After everything is written up and ready for submission, the last thing the group will need to do is fill out the [CONTRIBUTIONS.md]{.monospace} file.
By default, the file looks like this:

```markdown
# Contributions to group submission

## Editor: FirstName LastName Member 1

*   Questions answered:

## FirstName LastName Member 2

*   Questions answered:

## FirstName LastName Member 3

*   Questions answered:

## FirstName LastName Member 4

*   Questions answered:

```

At a minimum, you must remove the [FirstName LastName Member]{.monospace} entries in the template and fill in the names of the people in your group, indicate which group member served as the editor, and state which questions were written up by each member.

Additional information beyond this **should** be supplied, such as indicating when a group member helped another group member edit an answer or gave helpful comments in a Slack discussion.
For example, one group member's contribution list may read as follows:

```markdown
## Jane Smith

*   Questions answered: 4, 5, 6
*   Helped with editing on answers 8 and 9
*   Collaborated with group member Jack Williams on answering question 10
*   Pointed out spelling errors and suggested fixes to the document layout in the merged group document
```

## Working with a GitHub repository as a group

You will likely encounter some issues while working in a group-based GitHub repository.
In particular, you might find that when you click *"Push"* in the **Git** tab of RStudio, that it doesn't seem to work and instead you get an annoying error message!
This will happen when another member of your group has uploaded work before you did.
While this can be irritating to deal with, this is actually a good thing, as it is GitHub's way of protecting your files from accidential overwrites and deletions.

So what should you do to keep things running smoothly?
First, **always** work in your own file, never in another person's file.
If you are not the editor, then you should not edit [homework\_2\_group.Rmd]{.monospace} either!
Also, do not remove or rename any files that are not your own.
Finally, when you are getting ready to work, following the procedure below should help keep the error messages to a minimum:

1.  When you start working, you should begin by going to the **Git** tab and clicking *"Pull"* (notice this is not the same as *"Push"*).
    This will synchronize any new changes that your group may have made into your files.

2.  Work on your file as normal.
    When you have completed your work, save your file.

3.  Now we want to commit.
    **But first**, go to the **Git** tab and click *"Pull"* one more time to check for any other changes.
    Then, still in the **Git** tab, click the checkmark next to your updated file, type a message in the messagebox, and click the **Commit** button.
    
4.  If the updated file is no longer in the list of files in the **Git** tab, then your commit was successful.

5.  Click *"Push"* to upload your changed file.

### If the above advice doesn't work...

If, even after following the advice below, you still encounter error messages when Pulling from and Pushing to GitHub, please post about it in your group's private Slack channel.
Be sure to tag me using [\@Dr. Glasbrenner]{.monospace}.

## How to submit

When you are ready to submit, be sure that everyone in your group has committed and pushed their R Markdown files to Github.
The editor should do the following in RStudio Server:

1.  If it is not loaded already, open the RStudio project for the group homework assignment.

2.  Click on the **Git** tab in the upper-right window, then click *"Pull"* to make sure you have the latest version of all the files.

3.  Press <kbd>Ctrl</kbd>+<kbd>Shift</kbd>+<kbd>B</kbd> to knit the final submission to the PDF format.

4.  Download the PDF file to your computer.

5.  On Blackboard, find the **Homework 2 (Group)** submission link for your group.
    Submit the PDF for your group to lock in your submission time.

The editor should confirm that the files for their group's repository webpage on GitHub are fully up-to-date, and that if I were to knit the PDF file myself, it should be identical to what is uploaded to Blackboard.

::: {.callout .secondary}
**For the group submissions, you do not need to open up a Pull Request on GitHub.**
:::

## Cheatsheets

You are encouraged to review and keep the following cheatsheets handy while working on this assignment:

*   [RStudio cheatsheet][rstudio-cheatsheet]

*   [RMarkdown cheatsheet][rmarkdown-cheatsheet]

*   [RMarkdown reference][rmarkdown-reference]

*   [[ggplot2]{.monospace} cheatsheet][ggplot2-cheatsheet]

*   [Data transformation cheatsheet][data-transformation-cheatsheet]

*   [Data import cheatsheet][data-import-cheatsheet]

[ggplot2-cheatsheet]:             /doc/ggplot2-cheatsheet.pdf
[rstudio-cheatsheet]:             /doc/rstudio-IDE-cheatsheet.pdf
[rmarkdown-reference]:            /doc/rmarkdown-reference.pdf
[rmarkdown-cheatsheet]:           /doc/rmarkdown-cheatsheet.pdf
[github-classroom-repo]:          https://classroom.github.com/g/urOXDDJe
[data-import-cheatsheet]:         /doc/data-import-cheatsheet.pdf
[data-transformation-cheatsheet]: /doc/data-transformation-cheatsheet.pdf
